Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-25 prop_iop.tex
prop_iop.tex \section{Cryptodeterminism} Updating...

Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.

>>>>

\footnote{\yutsung{The word ''cryptodeterminism'' is used by A. Peres~\cite{peres1995quantum}.
However, he hasn't defined it explicitly so it is hard to tell how
to use it correctly...}}Although a real or interval-valued probability measure could be used
to model whether we believe an event will happen or not, the classical
world could be model in an simpler way. If the complete initial condition
for tossing a coin or throwing a needle is known, we can determine
whether an event will happen or not for sure~\cite{DiaconisHolmesMontgomery2007}.
In another word, Newtonian physics could be modeled by a cryptodeterministic
measure defined as follow.
